\chapter{Related Work}
\label{cha:relatedwork}

Revenue models that are applicable on the internet in order to monetize online content is a topic that has been actively researched and experimented with over the past few decades. This chapter dives into the related work on both a technical and an economical level. It is structured in a way so that three different research areas will be discussed. Firtsly, the economic aspects of unpaid content are reviewed. Secondly, an overview of the technical solutions to the unpaid content is given. This includes both micropayments, subscription models and online advertising. Lastly, the possiblities that arise in the blockchain era are discussed.


\section{Technical solutions}

In order to generate revenue from online content, there are two technical solutions broadly adopted: (micro)payments and online advertising. 

\subsection{Online advertising}
Advertising is a method to draw attention to a product, service or event in order to promote sales or attendance. Since the early days of the word wide web, this industry has also expanded to the internet. The first advertisement on the world wide web is possibly from 1994 on HotWired.com, which was bought by AT\&T and had a click through rate of 44\% \cite{firstbanner}. Meanwhile, the online advertising industry is very profitable and has evolved into the core business of the world wide web.

This section gives an overview of the current role model of the online advertisement industrsy and takes a closer look at the different approaches in online advertising and their privacy aspects. Lastly, the research field of privacy-friendly alternatives will be discussed. 

Normally, there are sereval parties involved in the advertising ecosystem. On one side, there is a publisher, such as \textit{Der Spiegel} that provides online content, for example: news articles. On the other side, there is an advertiser that provides the advertisement.

The most interesting part, however, is the ad platform. Ad platforms are entities that connect the publisher with the advertiser by providing them an interface to match both demand and supply. Due to the wide range of different publishers and users that are reached by ad networks, it becomes really efficient to allocate ad space. Ad platforms can even be considered as the central hub in the online advertising industry. When a user visits the website of a publisher, the browser communicates with the webserver. The browser receives the content that is displayed to the user. Along with this content, additional scripts that are associated with an ad network are also delivered to the browser and executed. These scripts are triggering a connection to the ad exchange. The ad platform is able to serve extra commercial content (advertisements) over this connection, which is embedded into the page by the script. This method makes it possible for ad exchanges to partner up with huge amounts of publishers and serve an amount of users that is several orders of magnitudes higher \cite{estrada2017online}.

The ad platform itself, consist of multiple components, that might also be run by different entities. Firstly, there is an ad network, which resells the ad space from a publisher to an advertiser. Secondly, another component on the ad platform is the ad exchange. These are auction based advertisement marketplaces where advertisers can bid on ad space in realtime, which means that the auction takes place when the user visits the website of the publisher. Based on the profile of the user, certain advertisers might be more interested to buy the ad space and thus offering a higher price \cite{estrada2017online}. 

Thirdly, a data aggregator is an entity that which goal is to gather and aggregate data about the purchasing interest of the users. This data is used to provide insights to both the advertisers and the publishers to target their marketing decisions \cite{estrada2017online}.

% privad
\subsubsection{Privad}
The problem with the infrastructure mentioned above, is that everything can be controlled by one single entity. This single entity knows everything about all parties involved: advertisers, publishers and users. The behavior of a single user is tracked across multiple websites, which might be considered a privacy concern. Guha et al. \cite{guha2011privad} developed Privad, which they call a practical private online advertising system. 

The model of Privad is slightly different from the original online advertising role model. The model also includes the user, publisher and advertiser. However, in this model there are also a dealer and a broker present. One key difference compared to the traditional online advertising model is that the profiling (building a profile of the user based on interests) is done on the users' computer and not by a central data aggregator. Secondly, the ad platform is split into two different entities: the broker and the dealer. The broker is comparable to the traditional ad platform and matches the profile with advertisements. The request, however does not come from the users' computer immediately: there is a dealer placed in between. The dealer anonymizes every request before it is sent to the broker and makes sure that click fraud is prevented. The dealer cannot eavesdrop on the request, because the request is sent in an encrypted form to the broker \cite{guha2011privad}. 

One concern with this approach is that a profile might be so detailed that the broker is able to find out an identity based on the profile. In orde to tackle this problem, Privad subscribes to a certain general profile that is shared with multiple other users. The user receives multiple advertisements and can pick locally which suits best.

Trust, however is still a key element in this approach. There is no way to find out if the dealer is trustworthy. If the dealer and the broker are secretly run by the same entity, it is possible to exchange data and learn more about the user. 

\subsection{Fee-based}

The second business model as an alternative to online advertising is requiring payments in exchange for content. This section describes what different approaches there are in the field of online payments, subscription models and third parties offering these services.

\subsubsection{Paywalls}

Even in the early days of the World Wide Web, the phenomenom of content that is only visible with a subscription existed. Such a mechanism, is called a paywall. For example, the \textit{Wall Street Journal} implemented already a hard paywall in 1996, which is still in place today, with over 2 million subscribers as of February 2020 \cite{firstpaywall}. 
Alternatives to hard paywalls are soft paywalls. The difference between both types is that soft paywalls are trying to convince potential customers to subscribe by giving them a free sample of the content. For example, the \textit{New York Times} has implemented a soft paywall with a limit of 5 free articles per month \cite{cook2012paying}.

% Salwen, Michael B.; Garrison, Bruce; Driscoll, Paul D. (2004). Online News and the Public. Routledge. p. 136. ISBN 978-1-135-61679-3.

Paywalls, however, are fairly easy to circumvent. This is especially the case for soft paywalls. Therefore, publishers are trying to implement counter measures in order to enforce a subscription. For example, the \textit{New York Times} attacked one popular circumvention method: the use of an incognito window. With behavioral analysis, it is possible to find out that the user is using an incognito window, which enables the \textit{New York Times} to prevent the free article from being served \cite{troupson2015yes}.  

\subsubsection{Micropayments}



\subsection{Donation-based}

Other publishers are relying on the willingness of their users to compensate. These systems are either implemented on one particular website or offered as a service over multiple websites. 

The Wikimedia Foundation is an example of a non-profit organiation that actively asks for donations on their Wikipedia website. However, this is not the main source of their revenue, because big companies like Amazon or Google are also donating to the foundation. Wikimedia raised a total of 91M USD in 2016-2017. \cite{wikimediadonation}

For smaller websites, such a campaign is not very viable. Users are not likely to send a donation to each individual contentmaker they support. For these smaller publishers, Flatter\footnote{\url{https://flatter.com}} offers a user experience which is similar to the Facebook-like button. Although, the difference is that instead of just showing the interest in a certain page of website, the button also shows appreciation by making a small micropayment. Flatter offers a subscription with a minimum of 2 EUR per month. This monthly subscription fee is divided amongst all websites the user clicked the Flatter-button on \cite{loll2010flattr}.







\section{Blockchain}

Blockchain technology has been with us for more than a decade. Satoshi Nakamoto built the first practical application that used the so called blockchain as a decentralized ledger, where it is possible to transfer a digital currency without trusting a single party \cite{nakamoto2019bitcoin}. Since then, a lot has changed and all kinds of experiments using this technology are performed. For example, blockchain implementations are now capable of running scripts which are even Turing complete, which opens the door to programmable money \cite{wood2014ethereum} and all kinds of other assets that are stored on the blockchain. 


\subsection{Lightning Network}
The general problem with blockchain technology is scalability and speed: the current average confirmation time of a bitcoin transaction takes a couple of minutes \cite{bamert2013have}. With the current blocksize of 1MB, the amount of transactions is limited at 7 per second. These limitations are preventing the use of this technology for micropayments: payments with a value less than a dollar \cite{definitionmicropayment}.

In order to solve this problem, several researchers have experimented with alternative ways to circumvent these issues. The most promising system in this research field is the lightning network. The goal of the lightning network is to send small payments immediately, without intervention of the blockchain ledger and with minimal fees. The lightning network features such a system by combining a smart idea with the capabilities of multi signature addresses. The system relies on two parties, for example Alice and Bob, opening a joint account (channel). Off chain, there is an agreement on which part of the joint account belongs to whom. With this joint account, Alice can transfer money to Bob and vice versa by just updating the agreement about the joint account. However, it is still not very practical if Alice also needs to open a joint account with any other party, for example Charlie, that she wants to transfer money to. The lightning network solves this issue by finding a path from Alice to Charlie using multiple joint accounts. In this example, it might be the case that Charlie has a joint account with Bob. Using this two joint accounts, Alice can transfer money indirectly to Charlie via Bob. In practice, this system follows a hubs and spoke model, where a couple of big players are connected to a lot of individuals in order to create a reliable network. Every hop that is used by a single transaction can also receive a small fee, but these fees are negligible compared to on-chain transactions \cite{poon2016bitcoin}.


\section{Automated payments}
In 2016, Brave Software launched a browser that blocked ads and trackers by default, the Brave Browser \footnote{\url{https://www.brave.com}}. During the introduction, Brave Software also shared their plans for a Brave Publisher Ads program to pay publishers back fair a share of internet revenue. As of 2020, their service is called "Brave rewards program", and any content creator can enroll in order to get paid for content. 

\subsection{Brave rewards} 
In order to achieve a system that makes it possible to reward content makers on the internet, Brave introduced the Basic Attention Token. This token, which works like any other cryptocurrency, represents user attention. Their goal with this token is to trade "attention" just like any other commodity, like oil and coffee. This means that the this token can also be traded on a cryptocurrency exchange. Brave Software is promoting this token to use it to reward internet users. What happens is that the brave brower is equipped with a standard ad blocker. The websites nevertheless, are filled with sponsored content by the brave browser. The difference with the original advertisements is that the user gets rewarded for viewing them in the BAT-token. The BAT-token can be traded for other crytocurrencies or even fiat currencies. 

For this thesis, another application of the BAT-token is more interesting. The systems actually also works the other way around: users can spend their BAT-tokens on the websites of the publishers they support in an automated manner. The remainder of this section shows the inner working of this system and explains why this is still suboptimal from a decentral perspective. First of all, the concept of the Brave Vault is explained. Secondly, the privacy and anonymity measures are analysed. Lastly, the monolopy of Brave in this ecosystem is discussed.

The Brave Vault is a private datastore where browsing information is stored. The central part in this Brave Vault is the \textit{persona}, that is used to identify and set your browsing behavior. The \textit{persona} can also be synced with other browsers, so that one user still uses the same profile when switching devices. Another part of the Brave Vault is the \textit{session}. The \textit{session} is bound to the browser and does not have a predefined lifetime. Browser dependant information, like browsing history is stored here \cite{brave-vault}.

In the \textit{persona}, there is a setting that states that the user wishes an ad-free browsing experience along with a contribution amount. The contribution amount is divided among the websites that the users visits. However, if these contributions are sent to the publishers directly, it would be very hard to guarantee privacy and anonymity. Based on the contributions, it is possible to reconstruct a profile that might be linked to an individual. To tackle these privcay concerns, Brave developed the Brave Ledger. The Brave Ledger is a central system that processes micropayments for the contributions to the publishers. The system is designed on two core principles: anonymous and accountable. This means that Brave should not be able to correlate publisher visits with contributions and Brave should only be able to have insights in the contributions on a an aggregated basis.

In order to build a system on these principles, statistical voting combined with an anonymous voting scheme is applied. First of all, statistical voting means that if you only have one vote, but you would like to vote on multiple choices, you are picking a choice at random out of your preferred choices. If everyone follows this system, the result of the election would roughly the same as if everyone had multiple votes. The advancement of such a system combined with making contributions to certain publishers, is that the user is not revealing his entire browsing history, but only one publisher that he wants to reward. Secondly, the Brave Ledger makes use of a anonymous voting scheme called ANONIZE2. Such a system guarantees that every single user in a group of users is able to cast a maximum of one vote, while keeping the vote anonymous.







\subsubsection{ICO}
% https://bravenewcoin.com/insights/basic-attention-token-price-analysis-publishers-increasing-across-all
Brave Software used an initial coin offering to introduce the new token to the market. The ICO happened in May 2017 and raised 156,000 ETH, which was worth around 35M USD at the time. The raised money is mostly used to pay for the development and other costs of the token. The development team exists out of 20 developers.


